Hierarchically Supervised Latent Dirichlet Allocation

### 2011-06-02 paper/experiments.tex
minor updates to many sections

We evaluated model performance for all three models with a range of
values for $\mu$, the mean prior parameter for regression parameters 
($\mu\in\left\{ -3,-2.8,-2.6,\ldots,1\right\}$). The number of topics for all
models was set to 50, the parameters for the prior distributions
$\alpha$, $\alpha^prime$, and $\gamma$ were a shape parameter of 1
and a scale parameters of 1000.

>>>>

We evaluated model performance for all three models with a range of
values for $\mu$, the mean prior parameter for regression parameters 
($\mu\in\left\{ -3,-2.8,-2.6,\ldots,1\right\}$). The number of topics for all
models was set to 50, the prior distributions of
$p\left(\alpha\right)$, $p\left(\alpha^{\prime}\right)$, and $p\left(\gamma\right)$ were gamma distributed with a shape parameter of 1
and a scale parameters of 1000.

### 2011-06-02 paper/model.tex
minor updates to many sections

The second half of step 4 is a substantial part of our contribution to the general class of supervised LDA models.  Here each document is generatively labeled using a hierarchy of conditionally dependent probit regressors \cite{gelman?,probit_regression?}.  For every label $l \in \mathcal{L}$ both the empirical topic distribution for document $d$ and whether or not its parent label was applied (i.e.~$\mathbb{I}(y_{\mathrm{pa}(l),d}=1)$) are used to decide whether or not  label $l$ is to be applied to  document $d$ as well.  Note that label $y_{l,d}$ can only be applied to document $d$ if its parent label $\mathrm{pa}(l)$ is also applied (these expressions are specific to is-a constraints but can be modified to accommodate different constraints).  The regression coefficients $\boldsymbol\eta_l$ are independent a priori, however, the hierarchical coupling in this model induces a posteriori dependence.   The net effect of this is that label predictors deeper in the label hierarchy are able to focus on finding specific, conditional labeling features.  We believe this to be a significant source of the empirical label prediction improvement we observe experimentally.  We test this hypothesis in Section~\ref{sec:experiments}.

>>>>

The second half of step 4 is a substantial part of our contribution to the general class of supervised LDA models.  Here each document is generatively labeled using a hierarchy of conditionally dependent probit regressors \cite{gelman?,probit_regression?}.  For every label $l \in \mathcal{L}$, both the empirical topic distribution for document $d$ and whether or not its parent label was applied (i.e.~$\mathbb{I}(y_{\mathrm{pa}(l),d}=1)$) are used to determine whether or not  label $l$ is to be applied to  document $d$ as well.  Note that label $y_{l,d}$ can only be applied to document $d$ if its parent label $\mathrm{pa}(l)$ is also applied (these expressions are specific to is-a constraints but can be modified to accommodate different constraints).  The regression coefficients $\boldsymbol\eta_l$ are independent a priori, however, the hierarchical coupling in this model induces a posteriori dependence.   The net effect of this is that label predictors deeper in the label hierarchy are able to focus on finding specific, conditional labeling features.  We believe this to be a significant source of the empirical label prediction improvement we observe experimentally.  We test this hypothesis in Section~\ref{sec:experiments}.

### 2011-06-02 paper/related_work.tex
minor updates to many sections

While there has been much work in multi-label classification of text and
text modeling in general, we focus here on topic modeling approaches.
Latent Dirichlet allocation (LDA) is a generative probabilistic model which
represents documents as a mixed-membership bag of word. Each document is
represented as a collection of words, generated from a set of topic assignments
(one for each word), where each topic assignment is drawn from a distribution
over topics~\citep{Blei2003}. sLDA is latent Dirichlet allocation (LDA)
\cite{Blei2003} augmented with per-document labeling, often taking the form of
a single numerical or categorical label. Examples of labels include rating
associated with an online  eview, grades for an essay, and number of times a
webpage is linked. This approach has been shown to outperform both LASSO
(L1 regularized least squares regression) and LDA followed by least
squares regression~\cite{BleiMcAuliffe2008}.

@@

In other work, researchers have classified documents in a hierarchy with naive Bayes classifiers
and support vector machines. Most of this work has been demonstrated on relatively
small datasets, small label spaces and has focused on single label classification without
a model of documents such as LDA\citep{mccallum99building,Dumais2000HCW,Kollerilprints291,Chakrabarti1998SFS}.

>>>>

While there has been much work in multi-label classification of text and
text modeling in general, we focus here on topic modeling approaches.
Latent Dirichlet allocation (LDA) is a generative probabilistic model which
represents documents as a mixed-membership bag of word. Each document is
represented as a collection of words, generated from a set of topic assignments
(one for each word), where each topic assignment is drawn from a distribution
over topics~\citep{Blei2003}. sLDA is latent Dirichlet allocation (LDA)
\cite{Blei2003} augmented with per-document labeling, often taking the form of
a single numerical or categorical label. Examples of labels include ratings
associated with online reviews, grades for essays, and the number of times a
webpage is linked. This approach has been shown to outperform both LASSO
(L1 regularized least squares regression) and LDA followed by least
squares regression~\cite{BleiMcAuliffe2008}.

@@

In other work, researchers have classified documents into a hierarchy with naive Bayes classifiers
and support vector machines. Most of this work has been demonstrated on relatively
small datasets, small label spaces and has focused on single label classification without
a model of documents such as LDA\citep{mccallum99building,Dumais2000HCW,Kollerilprints291,Chakrabarti1998SFS}.
